---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.retina = 2,
  fig.path = "figures/"
)
```

# A data-generation perspective on the use of multiple Fine--Gray models

<!-- badges: start -->
<!-- See hema review example-->
<!-- badges: end -->

**Authors**: Edouard F. Bonneville, Liesbeth C. de Wreede, and Hein Putter

## Abstract

Studies considering competing risks will often aim to estimate the cumulative incidence functions conditional on an individual's baseline characteristics. While the Fine--Gray subdistribution hazard model is tailor-made for analysing only one of the competing events, it may still be used in settings where multiple competing events are of scientific interest, where it is specified for each cause in turn. In this work, we provide an overview of data-generating mechanisms where proportional subdistribution hazards hold for at least one cause. We use these to motivate why the use of multiple Fine--Gray models should be reconsidered in favour of better alternatives.

## Usage

Two main files are of interest:

- [main.R](./main.R) - something something manuscript figs.
- [helpers.R](./helpers.R) - something something.

```{r tree-test, comment=NA, eval=FALSE, echo=FALSE}
.
├── analysis
│   ├── illustrative-example.R
│   ├── review-analysis.R
│   └── zotero-to-extaction-sheet.R
├── data
│   └── imps_all.rds
├── data-raw
│   ├── 2022-09-06_ris.ris
│   ├── dat-mds_admin-cens.fst
│   ├── data_dictionary.rda
│   ├── extraction-sheet.xlsx
│   └── literature-database-raw.csv
├── figures
│   └── journals-overview.svg
├── hema-missing-review.Rproj
├── R
│   └── forest-helper.R
├── README.md
└── README.Rmd
```

```{r tree-example, comment=NA, eval=FALSE, echo=FALSE}
# Or paste as test after
#fs::dir_tree(
#  regexp = "\\.html$|\\.Rmd$|\\.Rproj$|imgs|libs|old|css|slides", 
#  invert = TRUE
#)
```
